---
title: "tuesday-am-lidar"
author: "Catherine Hulshof DLP"
date: "June 21, 2016"
output: html_document
---
## Load required libraries

```{r load-libraries}

library(raster)
library(rhdf5)
library(rgdal)

```


## Import Canopy Height Model

```{r import-canopy-height }

chm <- raster("../NEONdata/D17-California/TEAK/2013/lidar/TEAK_lidarCHM.tif")
plot(chm,
     main = "this plots the image")
image(chm,
      main = "these are just piels and will stretch the space")
```

## Deal with 0 values
```{r assign-values-na }
hist(chm)
chm[chm==0] <- NA
hist(chm)
```

## Import aspect data
```{r import-aspect }
aspect <- raster("../NEONdata/D17-California/TEAK/2013/lidar/TEAK_lidarAspect.tif")
plot(aspect,
     main="Aspect data for Teakettle Field Site")
```

## Create classification matrix
```{r class-matrix }

class.m <- c(0, 45, 1,
             45, 135, NA,
             135, 225, 2,
             225, 315, NA,
             315, 360, 1)

rclm.m <- matrix(class.m,
           ncol = 3,
           byrow = TRUE)

rclm.m

```

## Reclassify raster
```{r reclassify-raster }
asp.ns <- reclassify(aspect,rclm.m)

plot(asp.ns, main = "North and South Facing Slopes")
```


# plot outside of the plot region

# make room for a legend
par(xpd = FALSE, mar=c(5.1, 4.1, 4.1, 4.5))
# plot
plot(asp.ns,
     col=c("white","blue","green"), # hard code colors, unclassified (0)=white,
		 #N (1) =blue, S(2)=green
     main="North and South Facing Slopes \nLower Teakettle",
     legend=F)
# allow legend to plot outside of bounds
par(xpd=TRUE)
# create the legend
legend((par()$usr[2] + 20), 4103300,  # set x,y legend location
       legend = c("North", "South"),  # make sure the order matches the colors, next
       fill = c("blue", "green"),
       bty="n") # turn off border
       

## Export Geotiff

```{r export-geotiff, eval = FALSE}

writeRaster(asp.ns,
            filename="../outputs/TEAK/Teak_nsAspect.tif",
            format="GTiff",
            options="COMPRESS=LZW",
            overwrite = TRUE,
            NAflag = -9999)

```

## Mask Raster will allow you to remove parts of a raster based on pixel values using a mask from an analysis. A mask raster layer is a layer that contains pixels that won’t be used in the analysis. In R, these pixels as assigned an NA value.

```{r raster-mask }

asp.ns

ndvi <- raster("../NEONdata/D17-California/TEAK/2013/spectrometer/veg_index/TEAK_NDVI.tif")
plot(ndvi,
     main = "NDVI for Teakettle field site")

#mask data
nFacing.ndvi <- mask(ndvi, asp.ns)
plot(nFacing.ndvi)

```

